An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-12-31 EconGrowth2.Rnw
Added two-column format for CD and LINEX scatter plots and spaghetti graphs. This is an enhancement on Issue #16.

<<Historical_Lattice_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
createHistoricalLatticeGraph()
@

@@

Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (without and with energy) resample models.

<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=cdTernaryGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (without and with energy) resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

@@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=cdSpaghettiGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
                                mapping=aes(delta, sigma), 
                                facet_formula=countryAbbrev~nest, 
                                alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelTernaryGraphHeight, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
standardTriPlot(data=cesTriPlotData)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.width=thirtySixPanelGraphWidth, fig.height=thirtySixPanelSpaghettiGraphHeight, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, level=1)
@

@@

<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with energy) resampling results.">>=
  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula= ~ countryAbbrev, alpha=0.05) +
      labs(x=expression(a[0]), y=expression(c[t])) +
       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

@@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX results.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
cesSpaghettiGraph(data=spagDataLinex, facet_formula= ~ Country, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

>>>>

<<Historical_Lattice_Graph, fig.pos="H", fig.width=maxWidth, fig.height=maxHeight, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
createHistoricalLatticeGraph()
@

@@

Figure~\ref{fig:CD_Ternary_Scatter_Graph} shows ternary plots 
for $\alpha$, $\beta$, and $\gamma$ parameter values 
for Cobb-Douglas (without and with energy) resample models.
Each reample is shown as a gray dot on the graph. 
The fit to historical data is shown as a gray circle.

@@

\twocolumn{}
<<CD_Ternary_Scatter_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Cobb-Douglas resample model parameters.">>=
  dataCD <- loadAllResampleData(modelType="cd", countryAbbrevsOrder=countryAbbrevsForGraph, energyType="none")
  dataCDQ <- loadAllResampleData(modelType="cde", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  data <- rbind.fill(dataCD, dataCDQ)
  standardTriPlot(data=data, facet_formula=countryAbbrev~energy)
@

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.75, fig.cap="Cobb-Douglas fitted models.">>=
cdData <- loadCDSpaghettiGraphData(energyType="none")
cdQData <- loadCDSpaghettiGraphData(energyType="Q")
cdData <- rbind(cdData, cdQData)
cesSpaghettiGraph(data=cdData, facet_formula=Country~Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}

@@

<<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
cesQResampleData <- loadCESResampleData(nest="all", energyType="Q")
standardScatterPlot(data=cesQResampleData, mapping=aes(gamma_coef, lambda), facet_formula=countryAbbrev~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
standardScatterPlot(data=cesQResampleData, mapping=aes(delta_1, sigma_1), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
standardScatterPlot(data=subset(cesQResampleData, nest!="(kl)"), 
                    mapping=aes(delta, sigma), facet_formula=countryAbbrev~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models.">>=
cesTriPlotData=loadCESResampleData(energyType="Q", nest="all")
standardTriPlot(data=cesTriPlotData)
@

@@

<<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8, fig.cap="CES fitted models.">>=
spagData <- loadCESSpaghettiGraphData(energyType="Q", nest="all")
cesSpaghettiGraph(data=spagData, facet_formula=Country~nest, level=spaghettiGraphLevel)+
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@

<<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
cesSpaghettiGraph(data=subset(spagData, Country=="CN" & nest=="(kl)e"), level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
@

@@

@@

\twocolumn{}
<<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
  linexResampleData <- loadAllResampleData(model="linex", energyType="Q", countryAbbrevsOrder=countryAbbrevsForGraph)
  standardScatterPlot(data=linexResampleData, aes(a_0, c_t), facet_formula=countryAbbrev~energy, alpha=0.05) +
      labs(x=expression(a[0]), y=expression(c[t])) +
       scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
       scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
@

<<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
spagDataLinex <- loadLinexSpaghettiGraphData(energyType="Q")
cesSpaghettiGraph(data=spagDataLinex, facet_formula=Country ~ Energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@
\onecolumn{}
